---
title: "linear model from Web"
author: "Bella Verdin"
date: "Spring 2024"
output:
   html_document:
         toc: true
         toc_depth: 5
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```


#Introduction
We will produce three equation models to get 
1. sim score based on arm strength 
2. sim score based on grip strength 
3. sim score based on arm and grip strength

For each model we will predict sims for arm=88,grip=94

#Method 
We have numerical response (sims score) and numerical explanatory variables (arm and grip strength)

So we use the Numerical-Num helper file 

## Model 1 SIM~ARMS

### scatterplot

```{r}
plot(SIMS~ARM,data=data)
```

the graph shows a positive relationship between SIMS and ARM. For it to be a positive linear relationship then all of the plots would be in a straight line, and the correlation could be around 0.8.

### Numerical results

```{r}
cor(SIMS~ARM,data=data)
```

The degree of correlation between arm strength and sims score. a strong correlation is 1 and a weak correlation would be 0. 

### Inferential  (Build model.1)

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

The p-value for the coefficient of arm is smaller than .05. that would mean that the coefficient is highly significant. 


#### Predict at target point

```{r}
SIMSpredict= predict.lm(model.1, newdata= data.frame(ARM=88,GRIP=94), interval = "confidence") 
print(SIMSpredict)
```

The prediction for ARM= 88, GRIP=94 is 0.71.

#### scatterplot with model fit

```{r}
plot(SIMS~ARM,data=data)
abline(model.1, col="red")
```

This is a scatter plot with a function on it. for ARM strength at 88 the 95 percent confidence interval should be between .48 and .92.

## Model 2 SIM~GRIP

### Now add in scatterplot

```{r}
plot(SIMS~GRIP,data=data)
```

it shows a positive relationship between SIMS and ARM. they would have to be in a straight line for it to be a perfect linear relationship. 

### Numerical results 

```{r}
cor(SIMS~GRIP,data=data)
```

This shows a correlation between sims score and grip. 1 being a strong correlation and 0 being weak

### Inferential  (Build model.2)
  
```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
```

The p-value for the coefficient of arm is shown smaller than .05. Which means that the coefficient is highly significant. 

#### predict model.2 at target point

```{r}
SIMSpredict= predict.lm(model.2, newdata= data.frame(ARM=88,GRIP=94), interval = "confidence") 
print(SIMSpredict)
```


#### now add the model fit to our plot for model.2
  
## Model 3 SIM~ARM+GRIP

### Numerical results (cor)

```{r}
m = data.frame(data['GRIP'],data['ARM'],data['SIMS'])
cor(m)
```

This table shows that SIMS correlates with GRIP in a positive way, (0.64) and SIMS correlates with ARM positively too, (0.69). these variables are shown as useful in predicting SIMS. 
  
```{r}
plot(data$GRIP, data$ARM)
```
  
This table shows that SIMS correlates with GRIP in a positive way, (0.64) and same with ARM (0.69). These are useful variables. 


### Inferential  (Build 2-dimentional model.3)

#### predict model.3 at target point
  

## Comparing nested models ANOVA Test

### Model.1 vs Model.3
### Model.2 vs Model.3

## Informally compare Model.1 with model.2

